Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-12-22 demystify.tex
updates

\myepigraphsimpsons{``Ay caramba!''}

@@

Here are the typical steps: (i) a faculty suspecting a cheating case will report it to the Office of Academic Integrity (OAI) at the university---the report often has supporting evidence and suggested penalty (e.g., a failing grade);  (ii)  OAI will completely take over and investigate the case independently (the prof. is not involved); and (iii) OAI will make the final decision.  It is important to note that after receiving the report from your prof., OAI \emph{completely} takes over and makes its own decision.  This means begging your professor will not help because they simply are no longer involved in the case and cannot do much.

>>>>

\myepigraphsimpsons{``As intelligent as you are, you have to learn to appreciate other points of view.''}

@@

Here are the typical steps: (i) a faculty suspecting a cheating case will report it to the Office of Academic Integrity (OAI) at the university---the report often has supporting evidence, e.g., a copy of the exam or assignment; (ii) OAI will investigate the case, e.g., by interviewing the student and faculty, and checking the evidence; (iii) OAI will make a decision, e.g., whether the student is guilty or not; and (iv) if guilty, OAI will decide on the punishment, e.g., a failing grade for the assignment or exam, a failing grade for the course, or even expulsion from the university, especially for repeat offenders.

So after receiving the report from your prof., OAI \emph{completely} takes over and makes its decision. This means begging your professor will not help because they simply are no longer involved in the case and cannot do anything.
